EGALITARIAN ASPECTS OF SCALE-FREE NETWORKS

### 2017-08-20 article/article.tex
arrumada capitalizacao da primeira letra
reworked the structure

\keywords{\em{ complex networks, scale-free networks, statistical physics, egalitarianism, Erdös sectors}}

@@

\subsection{Contextualization and related work}\label{sec:rel}
The complex network literature stresses concentration and often revolves around the hub. 
More accurately, it glamorizes the most connected nodes as
``both the strength and the weakness of scale-free networks''~\citep{wikipedia,networks},
and places them as the most important vertexes.
In this work, we argue that this is naive for a number of reasons.
In social networks terms, often used for such discussions:
\begin{itemize}
    \item Hubs are but a few vertexes, which are replaced constantly.
    \item Hubs present the most trivial behavior:
	    they interact as much as possible, in every situation, with every other agent.
		That is a prerequisite for they to be hubs.
    \item Hubs tend to present corrupt behavior,
	    as they apply huge amounts of time and energy (resources)
		on the network where it is a hub and frequently depend on such activity for basic provision.
		This might also be seen as a tendency of the hub to have a committed attitude,
		but given that hubs are also ubiquitous in non-professional networks,
		this might be understood as corrupt behavior by the non-warned.
    \item World input to the network is done mostly by peripheral and intermediary agents,
	    as they do not apply all their energy on the network.
    \item Authorities are often intermediaries or less active hubs,
	    especially in cases where they deliver quality, not quantity.
		This can be noticed by the fact that authorities usually exploit their authority
		in order to achieve their goals by means of the dedication of other agents.
	\item Network structure is yield by intermediary vertices~\citep{fabbri2},
	    as they are the only with non-trivial behavior:
		peripheral vertexes interact only a few times; hubs interact everywhere possible.
\end{itemize}

Therefore, this document is countercurrent with respect to available literature:
not only the focus here is to observe scale-free networks egalitarian aspects,
but also to dilute the hubs boast.
No academic writing was found by the authors to expose this simple and pertinent content.

@@

\section{EXALTATION OF HUBS AND DELUSIONS OF GRANDEUR}\label{sec:delusion}
The hubs, defined as the nodes with the greatest number of links in a scale-free network,
are reported in many studies as being the most relevant components.
In fact, selective attacks to the hubs (generally modeled as removing them)
cause the networks to loose many of the properties that make scale-free networks
appealing: the low average-distance between nodes, the fast transmission of information
and other sorts of transportation~\citep{networks}.
Nevertheless, aging of hubs is a recognized phenomenon,
i.e. the descent of the most connected hubs is observed
and even expected~\citep{aging}.
Also, diseases spread rapidly by means of the hubs 
and there are many other important negative contributions
of the hubs and important positive contributions of the
other vertices, as exposed in Section~\ref{sec:rel}.
In summary, the constant exaltation of the hubs in current
complex networks literature seems to be related to the
fact that the field is still incipient.
A psychologist might also add that it is related to
delusions of grandeur which affect a great fraction of
our society and thus leaks into the scientific tradition.
A social scientist might add that there is a constant
pressure performed by the more powerful and rich groups
to legitimate themselves and the inequality as a natural tendency.
Anyway, there is an evident consonance between the
constant ennoblement of the hubs, the stress on the association
of scale-free networks and inequality,
and our observation that these associations should be
considered with parsimony.

\section{ANTITHESIS}\label{sec:anti}

>>>>

\keywords{\em{ Complex networks, Scale-free networks, Statistical physics, Egalitarianism, Erdös sectors}}

@@

The complex network literature stresses concentration and often revolves around the hub. 
More accurately, it glamorizes the most connected nodes as
``both the strength and the weakness of scale-free networks''~\citep{wikipedia,networks},
and places them as the most important vertexes.
In this work, we argue that this is naive for a number of reasons.
Therefore, this document is countercurrent with respect to available literature:
not only the focus here is to observe scale-free networks egalitarian aspects,
but also to dilute the hubs boast.
No academic writing was found by the authors to expose this simple and pertinent content.

Section~\ref{sec:can} presents a glimpse at standard theory related to power laws.
Section~\ref{sec:three} states the aspects of scale-free networks that are egalitarian.
Section~\ref{sec:delusion} considers also the hubs, intermediary and peripheral vertices
and a probable unbalance current literature has in considering the importance of these sectors.
Section~\ref{sec:con} is dedicated to conclusions and future work.

@@

\section{EXALTATION OF HUBS AND DELUSIONS OF GRANDEUR}\label{sec:delusion}
The hubs, defined as the nodes with the greatest number of links in a scale-free network,
are reported in many studies as being the most relevant components.
In fact, selective attacks to the hubs (generally modeled as removing them)
cause the networks to loose many of the properties that make scale-free networks
appealing: the low average-distance between nodes, the fast transmission of information
and other sorts of transportation~\citep{networks}.
Nevertheless, aging of hubs is a recognized phenomenon,
i.e. the descent of the most connected hubs is observed
and even expected~\citep{aging}.
Also, diseases spread rapidly by means of the hubs 
and there are many other important negative contributions
of the hubs and important positive contributions of the
other vertices.
In social networks terms, often used for such discussions:
\begin{itemize}
    \item Hubs are but a few vertexes, which are replaced constantly.
    \item Hubs present the most trivial behavior:
	    they interact as much as possible, in every situation, with every other agent.
		That is a prerequisite for they to be hubs.
    \item Hubs tend to present corrupt behavior,
	    as they apply huge amounts of time and energy (resources)
		on the network where it is a hub and frequently depend on such activity for basic provision.
		This might also be seen as a tendency of the hub to have a committed attitude,
		but given that hubs are also ubiquitous in non-professional networks,
		this might be understood as corrupt behavior by the non-warned.
    \item World input to the network is done mostly by peripheral and intermediary agents,
	    as they do not apply all their energy on the network.
    \item Authorities are often intermediaries or less active hubs,
	    especially in cases where they deliver quality, not quantity.
		This can be noticed by the fact that authorities usually exploit their authority
		in order to achieve their goals by means of the dedication of other agents.
	\item Network structure is yield by intermediary vertices~\citep{fabbri2},
	    as they are the only with non-trivial behavior:
		peripheral vertexes interact only a few times; hubs interact everywhere possible.
\end{itemize}

In summary, the constant exaltation of the hubs in current
complex networks literature seems to be related to the
fact that the field is still incipient.
A psychologist might also add that it is related to
delusions of grandeur which affect a great fraction of
our society and thus leaks into the scientific tradition.
A social scientist might add that there is a constant
pressure performed by the more powerful and rich groups
to legitimate themselves and the inequality as a natural tendency.
Anyway, there is an evident consonance between the
constant ennoblement of the hubs, the stress on the association
of scale-free networks and inequality,
and our observation that these associations should be
considered with parsimony.
